---
title: "Lake Nebagamon Ice, 1943-2021"
author: "Derek Ogle"
date: today
format: 
  html:
    embed-resources: true
    code-fold: true
    code-line-numbers: true
    df-print: kable
fig-cap-location: bottom
tbl-cap-location: top
evaluate:
  warning: false
---

## Setup
The following code loads relevant packages and prepares the ice-in^[Earliest date where lake is completely covered until the following spring.] and ice-out^[Earliest date where lake is completely devoid of ice in the spring.] dates data for [Lake Nebagamon](https://dnr.wi.gov/lakes/lakepages/LakeDetail.aspx?wbic=2865000), WI from 1943 to 2021 as recorded by citizen observers.^[Data were provided to me by Gary Hagstrom who received the data from XXX. The original data acknowledged J Arthur, G DeBrunye, W Kiefer, A Mack, M Laskkowski, J Snydle.]

```{r setup}
#| message: FALSE
#| results: "hide"

source("iceHelpers.R")

dat <- prepIceData(sheet="Nebagamon")
sum <- sumIceData(dat) %>%
  mutate(inEarlyYr=dat$fyr[dat$inDay==inEarlyDay],
         inLateYr=dat$fyr[dat$inDay==inLateDay],
         outEarlyYr=dat$fyr[dat$outDay==outEarlyDay],
         outLateYr=dat$fyr[dat$outDay==outLateDay],
         durShortYr1=dat$fyr[dat$daysIced==durShort][1],
         durShortYr2=dat$fyr[dat$daysIced==durShort][2],
         durLongYr=dat$fyr[dat$daysIced==durLong])
```

## Ice In and Out Dates

The range for both ice-in (`r sum$inEarlyDate` to `r sum$inLateDate`) and ice-out (`r sum$outEarlyDate` to `r sum$outLateDate`) dates is considerable, at approximately six weeks for each (@fig-inouthist). There are *weak* indications for a slightly later ice-in date and, *possibly*, a slightly earlier ice-out date in the last two decades (@fig-inout).

```{r}
#| message: FALSE
#| label: fig-inouthist
#| fig-cap: Lake Nebagamon ice in and out dates.
#| fig-width: 8
#| fig-height: 4

p_inhist <- ggplot(data=dat,mapping=aes(x=inDay)) +
  geom_histogram(binwidth=5,boundary=0,fill=FSA::col2rgbt(inclr,0.5),color="black") +
  scale_y_continuous(expand=expansion(mult=c(0,0.02))) +
  scale_x_continuous(name="Day of Ice-In",
                     breaks=date_breaks2,labels=date_labels2) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        panel.grid.major.y=element_blank(),
        panel.grid.minor.y=element_blank())

p_inhist <- p_inhist +
  annotate(geom="text",hjust="left",color=inclr,
           x=-25,y=13,label=paste0("Average (",sum$inAvgDate,")")) +
  annotate(geom="curve",x=-25.5,y=13,xend=sum$inAvgDay,yend=0,
           linewidth=0.75,curvature=0.1,color=inclr,
           arrow=arrow(length=unit(3,"mm"),angle=20,type="closed"))

p_outhist <- ggplot(data=dat,mapping=aes(x=outDay)) +
  geom_histogram(binwidth=5,boundary=0,fill=FSA::col2rgbt(outclr,0.5),color="black") +
  scale_y_continuous(expand=expansion(mult=c(0,0.02))) +
  scale_x_continuous(name="Day of Ice-Out",
                     breaks=date_breaks2,labels=date_labels2) +
  theme(axis.title.y=element_blank(),axis.text.y=element_blank(),
        panel.grid.major.y=element_blank(),panel.grid.minor.y=element_blank())

p_outhist <- p_outhist +
  annotate(geom="text",hjust="right",color=outclr,
           x=97,y=13,label=paste0("Average (",sum$outAvgDate,")")) +
  annotate(geom="curve",x=97.5,y=13,xend=sum$outAvgDay,yend=0,
           linewidth=0.75,curvature=-0.1,color=outclr,
           arrow=arrow(length=unit(3,"mm"),angle=20,type="closed"))
p_inhist + p_outhist
```

```{r}
#| message: FALSE
#| label: fig-inout
#| fig-cap: Lake Nebagamon ice in and out dates by year.

p_inout <- ggplot(data=dat,mapping=aes(x=fyr)) +
  geom_smooth(mapping=aes(y=inDay),se=FALSE,color=inclr) +
  geom_smooth(mapping=aes(y=outDay),se=FALSE,color=outclr) +
  geom_ribbon(mapping=aes(ymin=inDay,ymax=outDay),fill=icefillclr) +
  geom_line(mapping=aes(y=inDay),linewidth=main_lw,color=main_clr) +
  geom_line(mapping=aes(y=outDay),linewidth=main_lw,color=main_clr) +
  geom_point(mapping=aes(y=inDay),size=1,shape=21,fill="white") +
  geom_point(mapping=aes(y=outDay),size=1,shape=21,fill="white") +
  scale_y_continuous(breaks=date_breaks1,labels=date_labels1,
                     expand=expansion(mult=0.08)) +
  scale_x_continuous(name="Ice Season Start Year",
                     breaks=yr_breaks10,minor_breaks=yr_breaks5,
                     expand=expansion(mult=0.01)) +
  theme(axis.title.y=element_blank(),
        panel.grid.minor.y=element_blank())

p_inout <- p_inout +
  annotate(geom="text",vjust=1.5,color=inclr,
           x=sum$inEarlyYr,y=sum$inEarlyDay,
           label=paste0("Earliest (",sum$inEarlyDate,")")) +
  annotate(geom="text",vjust=-0.5,color=inclr,
           x=sum$inLateYr-2,y=sum$inLateDay,
           label=paste0("Latest (",sum$inLateDate,")")) +
  annotate(geom="text",vjust=1.5,color=outclr,
           x=sum$outEarlyYr,y=sum$outEarlyDay,
           label=paste0("Earliest (",sum$outEarlyDate,")")) +
  annotate(geom="text",vjust=-0.5,color=outclr,
           x=sum$outLateYr,y=sum$outLateDay,
           label=paste0("Latest (",sum$outLateDate,")")) +
  annotate(geom="point",x=1942.5,y=sum$outAvgDay,
           shape="-",color=outclr,size=10) +
  annotate(geom="point",x=1942.5,y=sum$inAvgDay,
           shape="-",color=inclr,size=10) +
  annotate(geom="text",x=mean(dat$fyr),y=(122-61)/2,
           label=paste0("Average duration of ice is ",sum$durAvg," days"))

p_inout +
  annotate(geom="text",hjust="left",color=outclr,
           x=1947,y=75,label=paste0("Average Out (",sum$outAvgDate,")")) +
  annotate(geom="curve",x=1946.5,y=75,xend=1942.5,yend=sum$outAvgDay,
           linewidth=0.75,curvature=-0.3,color=outclr,
           arrow=arrow(length=unit(3,"mm"),angle=20,type="closed")) +
  annotate(geom="text",hjust="left",color=inclr,
           x=1947,y=0,label=paste0("Average In (",sum$inAvgDate,")")) +
  annotate(geom="curve",x=1946.5,y=0,xend=1942.5,yend=sum$inAvgDay,
           linewidth=0.75,curvature=0.3,color=inclr,
           arrow=arrow(length=unit(3,"mm"),angle=20,type="closed"))
```


## Ice Duration

Since 1943 the average days of ice coverage on Lake Nebagamon was `r sum$durAvg` days, though the range was considerable from `r sum$durShort` to `r sum$durLong` days (@fig-durhist). There is an indication that the length of ice duration has declined, on average, by a little over a week in the last two decades (@fig-dur). Seven of the ten shortest ice duration seasons have occurred since 2000 (@tbl-durShort), whereas only one of the ten longest ice duration seasons have occurred in that same time period (@tbl-durLong).

```{r}
#| message: FALSE
#| label: fig-durhist
#| fig-cap: Lake Nebagamon ice durations, 1943-2021.
#| fig-width: 5
#| fig-height: 4

p_durhist <- ggplot(data=dat,mapping=aes(x=daysIced)) +
  geom_histogram(bins=10,boundary=0,
                 fill=FSA::col2rgbt(icefillclr,0.5),color="black") +
  scale_y_continuous(expand=expansion(mult=c(0,0.02))) +
  scale_x_continuous(name="Days of Ice Coverage") +
  theme(axis.title.y=element_blank(),axis.text.y=element_blank(),
        panel.grid.major.y=element_blank(),panel.grid.minor.y=element_blank())

p_durhist +
  annotate(geom="text",hjust="left",
           x=155,y=13,label=paste0("Average (",sum$durAvg," days)")) +
  annotate(geom="curve",x=154.5,y=13,xend=sum$durAvg,yend=0,
           linewidth=0.75,curvature=0.2,
           arrow=arrow(length=unit(3,"mm"),angle=20,type="closed"))
```

```{r}
#| message: FALSE
#| label: fig-dur
#| fig-cap: Lake Nebagamon ice duration by year.

p_durat <- ggplot(data=dat,mapping=aes(x=inYr,y=daysIced)) +
  geom_smooth(color="darkred",se=FALSE) +
  geom_line(linewidth=main_lw,color=main_clr) +
  geom_point(size=1,shape=21,fill="white") +
  scale_y_continuous(name="Days Ice Coverage",
                     breaks=seq(110,180,10),
                     limits=c(108,175),
                     expand=expansion(add=5)) +
  scale_x_continuous(name="Ice Season Start Year",
                     breaks=yr_breaks10,minor_breaks=yr_breaks5,
                     expand=expansion(mult=0.01)) +
  theme(panel.grid.minor.y=element_blank())

p_durat +
  annotate(geom="point",x=1942.5,y=sum$durAvg,
           shape="-",color="black",size=10) +
  annotate(geom="text",hjust="left",color="black",
           x=1945,y=111,label=paste0("Average (",sum$durAvg," days)")) +
  annotate(geom="curve",x=1944.5,y=111,xend=1942.5,yend=sum$durAvg,
           linewidth=0.75,curvature=-0.1,color="black",
           arrow=arrow(length=unit(3,"mm"),angle=20,type="closed")) +
  annotate(geom="text",hjust="right",color="darkblue",
           x=1985,y=sum$durLong,label=paste0("Longest (",sum$durLong," days)")) +
  annotate(geom="segment",x=1985.5,y=sum$durLong,
           xend=sum$durLongYr,yend=sum$durLong,
           linewidth=0.75,color="darkblue",
           arrow=arrow(length=unit(3,"mm"),angle=20,type="closed")) +
  annotate(geom="text",hjust="right",color="darkred",
           x=2000,y=sum$durShort,label=paste0("Shortest (",sum$durShort," days)")) +
  annotate(geom="curve",x=2000.5,y=sum$durShort,
           xend=sum$durShortYr1,yend=sum$durShort,
           linewidth=0.75,curvature=-0.2,color="darkred",
           arrow=arrow(length=unit(3,"mm"),angle=20,type="closed")) +
  annotate(geom="curve",x=2000.5,y=sum$durShort,
           xend=sum$durShortYr2,yend=sum$durShort,
           linewidth=0.75,curvature=+0.2,color="darkred",
           arrow=arrow(length=unit(3,"mm"),angle=20,type="closed"))
```

```{r}
#| label: tbl-durShort
#| tbl-cap: Winter seasons with the 10 **shortest** ice durations.

tmp <- dat %>%
  select(season,inDate,outDate,daysIced) %>%
  mutate(inDate=format(inDate,"%b %e"),
         outDate=format(outDate,"%b %e"))

tmp %>% slice_min(order_by=daysIced,n=10) %>%
  rename("Season"=season,"In"=inDate,"Out"=outDate,"Duration"=daysIced)
```

```{r}
#| label: tbl-durLong
#| tbl-cap: Winter seasons with the 10 **longest** ice durations.

tmp %>% slice_max(order_by=daysIced,n=10) %>%
  rename("Season"=season,"In"=inDate,"Out"=outDate,"Duration"=daysIced)
```

