---
---

# Cash
We have had Cash since September 2020. He is a spirited "big pony" who loves to be outside, especially on [walks/hikes](hiking.html). The latest picture of Cash is below; [go here](Cash.html) to see a picture from (nearly) each week of his life.

```{r}
#| echo: false
#| results: asis
path <- "../zresources/img/Cash/"
imgs <- rev(list.files(path=path))[1]
caps <- stringr::str_replace(tools::file_path_sans_ext(imgs),"_"," ")
cat('![',caps,'](',path,imgs,'){width=50%}',sep="")
```
```{r}
#| echo: false
#| results: hide
quarto::quarto_render(input="Cash.qmd")
```


&nbsp;

# Jem
Jem graced our lives from April(ish) 2009 to almost August 2018. Many people knew Jem from seeing him around the Science Center during the school year. Jem was such a special dog ... very smart, incredibly loyal, and always watching over and protecting us. While he was a little snooty and often turned up his nose at "strangers", he also melted your heart if he decided to give you the time of day. [Here is a short piece that I wrote about Jem](http://sheltiespandp.weebly.com/jem.html) a few years ago.

Jem was taken from us way too early, though we know he is now with his ["grandpa owner"](http://www.apg-wi.com/ashland_daily_press/obituaries/lloyd-sellung/article_f4167abc-1e92-11e8-87a0-17b0ec3869f9.html) taking walks, sitting on the couch together, and scheming to get those chippies. RIP "poundy", I wish we would have had more time together, you were such a special little guy!! We will [see you again](https://www.youtube.com/watch?v=mj37_Rqsec4) (*Thanks [Ronnie](http://www.ronniebakerbrooks.com/) ... beautiful song*).

```{r}
#| echo: false
#| results: asis
gpxhelpers::makeCarousel(id="Jem",path="../zresources/img/Jem/",
                         width=50,captions=FALSE,controls=FALSE,interval=2000)
```

&nbsp;

# Jordan
Kim and I got Jordan soon in 1991, soon after we were married. "Jordo" enriched our lives until March 2006. We miss the walks and boat rides. RIP "Bordo Dog"!!!

```{r}
#| echo: false
#| results: asis
gpxhelpers::makeCarousel(id="Jordan",path="../zresources/img/Jordan/",
                         width=50,captions=FALSE,controls=FALSE,interval=2000)
```

&nbsp;

&nbsp;

# Sheltie Information

- [AKC Breed Information](https://www.akc.org/dog-breeds/shetland-sheepdog/)
- [AKC 7 Things to Know](https://www.akc.org/expert-advice/lifestyle/7-facts-shetland-sheepdogs/)
- [WebMD All You Need to Know](https://pets.webmd.com/dogs/what-to-know-shetland-sheepdogs)
- [Ulitimate Guide](https://therapypet.org/dog-breeds/shetland-sheepdogs/)
- [Shelties Purebred and Perfect](https://sheltiespandp.weebly.com/)
- [Wisconsin Shelties Rescue](http://www.wisheltierescue.com/)
