---
title: "TITLE HERE"
---

SAY SOMETHING HERE

```{r setup, include=FALSE}
#| label: setup
#| include: false
#| cache: true

# Make vector of colors for Iron River Area
clrs <- c("Highway"="#CC0000","Paved"="#336666",
          "Gravel"="#CC6600","Offroad"="#CC9900",
          "Trail"="#999933", "ATV"="#663300")

# Read in CSV file will all track info needed for the map
project <- "Iron River Area"
trkdat <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkdat.csv"))
trkinfo <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkinfo.csv"))

# Make the walk
walkIDs <- c("FR40007","FR40008","FR40009","FR39904","FR39801","FR400A01","BECK06")
awalk <- gpxhelpers::walkMaker(trkdat,trkinfo,walkIDs,findOrder=FALSE)

# Get photos
pix <- readxl::read_excel("c:/aaaPersonal/MAPPING/Data/Trail Mapping Info.xlsx",sheet="Photos")
walkPix <- gpxhelpers::walkGetPhotos(pix,walkIDs,"https://github.com/droglenc/MAPPING/raw/main/Images")
npix <- nrow(walkPix)
```

## Overview Map
The extent of this walk is highlighted by the blue box in this map.

```{r}
#| label: overviewMap
#| echo: false
gpxhelpers::allTracksMap(trkdat,clrs,walk=awalk,verbose=FALSE)
```

:::{.callout-info appearance="simple"}
## Map Key
See [Iron River Area Overview page](Iron River Area.html) for key to segment color coding.
:::

## Walk-Specific Map
```{r}
#| label: walkMap
#| echo: false
gpxhelpers::walkMap(awalk,clrs,verbose=FALSE)
```

:::{.callout-note appearance="simple"}
## Take Note
- Click on a segment to get specific information.
- Numeric labels correspond to the same labels in the elevation profile and summary information below.
:::

## Elevation Profile
```{r}
#| label: walkElevation
#| echo: false
gpxhelpers::walkElevation(awalk)
```

## Summary Information
```{r}
#| label: walkSummary
#| echo: false
gpxhelpers::walkSummary(awalk)
```


```{r results="asis"}
#| echo: false
#| results: asis
if (npix>0) cat("## Images from These Tracks")
i <- 1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

```{r}
#| echo: false
#| eval: !expr i<=npix
#| out.width: "50%"
#| fig.cap: !expr walkPix$Caption[i-1]
suppressWarnings(knitr::include_graphics(walkPix$Photo[i]))
i <- i+1
```

