---
title: "Ice Cave City Loop"
subitle: "Decorah"
---

A number of times while passing through [Decorah](https://visitdecorah.com/) we will take some sort of hike on the numerous nice trails in the city. Several times we start near Phelps Park on the Oneonta Trail and create a loop on the Ice Cave Rd by [Ice Cave State Preserve](https://www.iowadnr.gov/places-go/state-preserves/decorah-ice-cave-state-preserve) and [Dunning Springs Park](https://visitdecorah.com/trail/dunnings-spring-park/) circling back through town to our car. This is a pretty hike that is mostly along the river, though some woods, with fun sights at the cave and springs.

```{r setup, include=FALSE}
#| label: setup
#| include: false

# Make vector of colors for Iron River Area
clrs <- c("Highway"="#CC0000","Paved"="#336666",
          "Gravel"="#CC6600","Offroad"="#CC9900",
          "Trail"="#999933", "ATV"="#663300")

# Read in CSV file will all track info needed for the map
project <- "Iowa"
walkID <- "IA_ICECAVELOOP"
trkdat <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkdat.csv"))
trkinfo <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkinfo.csv"))

# Make the walk
walkIDs <- c("IADCRHONE01","IADCRHONE02","IADCRHFTH99","IADCRHICV01","IADCRHICV09",
             "IADCRHICV09","IADCRHICV02","DNGSP01","DNGSP02","DNGSP02",
             "DNGSP01","IADCRHICV03","IADCRHCLG99","IADCRHONE09","IADCRHONE01")
awalk <- gpxhelpers::walkMaker(trkdat,trkinfo,walkIDs,findOrder=FALSE)

# Get photos
pix <- readxl::read_excel("c:/aaaPersonal/MAPPING/Data/Trail Mapping Info.xlsx",sheet="Photos")
walkPix <- gpxhelpers::walkGetPhotos(pix,walkIDs,"https://github.com/droglenc/MAPPING/raw/main/Images")
npix <- nrow(walkPix)
```

## Walk-Specific Map
```{r}
#| label: walkMap
#| echo: false
gpxhelpers::walkMap(awalk,clrs,verbose=FALSE)
```

:::{.callout-note appearance="simple"}
## Take Note
- Click on a segment to get specific information.
- Numeric labels correspond to the same labels in the elevation profile and summary information below.
:::

## Elevation Profile
```{r}
#| label: walkElevationConstruct
#| echo: false
#| results: hide
fnm <- paste0("c:/aaaWork/Web/droglenc.github.io/personal/Hiking/elevs/",walkID,".png") 
png(fnm,width=7,height=5,units="in",res=216)
gpxhelpers::walkElevation(awalk)
dev.off()
```
```{r}
#| label: walkElevation
#| echo: false
knitr::include_graphics(fnm)
```

## Images
```{r}
#| echo: false
#| results: asis
gpxhelpers::makeCarousel(id="Walk",path="",
                         imgs=walkPix$Photo,caps=walkPix$Caption,
                         width=75,captions=TRUE,controls=TRUE,indicators=FALSE)
```

## GPX Download
```{r}
#| label: gpxdownload
#| echo: false
#| message: false
#| results: asis
fnm <- paste0(walkID,".gpx")
gpxhelpers::makeWalkGPX(pin=paste0("c:/aaaPersonal/MAPPING/Tracks/",project),
                              pout="c:/aaaWork/Web/droglenc.github.io/personal/Hiking/gpx",
                              fnm=fnm,
                              IDs=unique(walkIDs))
cat("A sanitized GPX file of our hike [is here](gpx/",fnm,").",sep="")
```

## Summary Information
```{r}
#| label: walkSummary
#| echo: false
gpxhelpers::walkSummary(awalk)
```
