---
title: "Barnes Barrens Loop 1"
---

On 1-Feb-2024 [Cash](../shelties.html#cash) and I walked a loop of forest "trails" in the Barnes Barrens. Our walk began at Halfway Rd to head north on a counter-clockwise loop that crossed Moore Rd, Halfway Rd again, Moore Rd again, before ending back at Halfway Rd. Generally the "inside" of the loop appears to be being managed for a barrens habitat (logged, slash removed, and burnt) whereas the "outside" of the loop varied in habit from a typical barrens look to a mix of scrubby oak and pine to some rather larger (planted) pines. This was not an overly beautiful hike but I like the open view of the barrens landscape. We did not see [Sharptail Grouse](https://dnr.wisconsin.gov/topic/hunt/sharptailgrouse) this day, but we have seen them when driving the section of Halfway Rd that bisects this hike. This hike was pretty easy walking (it could be driven with a 4WD truck). Details are below.

```{r setup, include=FALSE}
#| label: setup
#| include: false

# Make vector of colors for Iron River Area
clrs <- c("Highway"="#CC0000","Paved"="#336666",
          "Gravel"="#CC6600","Offroad"="#CC9900",
          "Trail"="#999933", "ATV"="#663300")

# Read in CSV file will all track info needed for the map
project <- "Iron River Area"
walkID <- "IRA_BBarrens1"
trkdat <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkdat.csv"))
trkinfo <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkinfo.csv"))

# Make the walk
walkIDs <- c("TRMR14","TRMR13","TRMR12","TRMR11","TRMR01","TRMR02","TRMR03",
             "TRMR04","TRMR05","TRMR06","TRMR07","TRMR08","TRMR09","TRMR10",
             "TRMR18","TRMR17","TRMR16","TRMR15")
awalk <- gpxhelpers::walkMaker(trkdat,trkinfo,walkIDs,findOrder=FALSE)

# Get photos
pix <- readxl::read_excel("c:/aaaPersonal/MAPPING/Data/Trail Mapping Info.xlsx",sheet="Photos")
walkPix <- gpxhelpers::walkGetPhotos(pix,walkIDs,"https://github.com/droglenc/MAPPING/raw/main/Images")
npix <- nrow(walkPix)
```

## Overview Map
The extent of this walk is highlighted by the blue box in this map.

```{r}
#| label: overviewMap
#| echo: false
gpxhelpers::allTracksMap(trkdat,clrs,walk=awalk,verbose=FALSE,map_bufr=0.0008)
```

:::{.callout-info appearance="simple"}
## Map Key
See [Iron River Area Overview page](Iron River Area.html) for segment color coding key and description for use of controls.
:::

## Walk-Specific Map
```{r}
#| label: walkMap
#| echo: false
gpxhelpers::walkMap(awalk,clrs,verbose=FALSE)
```

:::{.callout-note appearance="simple"}
## Take Note
- Click on a segment to get specific information.
- Numeric labels correspond to the same labels in the elevation profile and summary information below.
:::

## Elevation Profile
```{r}
#| label: walkElevationConstruct
#| echo: false
#| results: hide
fnm <- paste0("c:/aaaWork/Web/droglenc.github.io/personal/Hiking/elevs/",walkID,".png") 
png(fnm,width=7,height=5,units="in",res=216)
gpxhelpers::walkElevation(awalk)
dev.off()
```
```{r}
#| label: walkElevation
#| echo: false
knitr::include_graphics(fnm)
```

## Images
```{r}
#| echo: false
#| results: asis
gpxhelpers::makeCarousel(id="Walk",path="",
                         imgs=walkPix$Photo,caps=walkPix$Caption,
                         width=75,captions=TRUE,controls=TRUE,indicators=FALSE)
```

## GPX Download
```{r}
#| label: gpxdownload
#| echo: false
#| message: false
#| results: asis
fnm <- paste0(walkID,".gpx")
gpxhelpers::makeWalkGPX(pin=paste0("c:/aaaPersonal/MAPPING/Tracks/",project),
                        pout="c:/aaaWork/Web/droglenc.github.io/personal/Hiking/gpx",
                        fnm=fnm,
                        IDs2Add=unique(walkIDs))
cat("A sanitized GPX file of our hike [is here](gpx/",fnm,").",sep="")
```

## Summary Information
```{r}
#| label: walkSummary
#| echo: false
gpxhelpers::walkSummary(awalk,dropOwner=TRUE)
```

