---
title: "Iron River Area Hiking/Walking"
---

For exercise and for getting to know the area in which I have lived for the last three decades, [Cash](../shelties.html#cash) and I have been walking may of the roads and back-country trails in the [Iron River](https://visitironriver.com/) WI area. Below are the places we have walked thusfar. See the notes below the map for how to interact with the map. More information on specific walks can be accessed from [my main hiking page](../hiking.html).

```{r setup, include=FALSE}
#| label: setup
#| include: false
#| cache: true

## Run following two lines if new tracks have been added since last update
#source("c:/aaaPersonal/MAPPING/Scripts/dataPrepHelper.R")
#dat <- dataPrepHelper(project=project,basedir="c:/aaaPersonal/MAPPING/")

# Make vector of colors for Iron River Area
clrs <- c("Highway"="#CC0000","Paved"="#336666",
          "Gravel"="#CC6600","Offroad"="#CC9900",
          "Trail"="#999933", "ATV"="#663300")

# Read in CSV file will all track info needed for the map
project <- "Iron River Area"
trkdat <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkdat.csv"))
```

```{r}
#| label: makeMap
#| echo: false
#| fig.width: 7
#| fig.height: 7
gpxhelpers::allTracksMap(trkdat,clrs=clrs,verbose=FALSE)
```

#### Notes

* <span style="color: #CC0000">Red</span> is highway, <span style="color: #336666">Blue</span> is paved road, <span style="color: #CC6600">Orange</span> is gravel road, <span style="color: #CC9900">Yellow</span> is offroad (ATV but possible 4WD vehicle), <span style="color: #999933">Green</span> is trail (hiking but some ATV), and <span style="color: #663300">Brown</span> is designated ATV/Snowmobile (only) trail.
* Hover on track to see track abbreviation.
* Click on track to get track information.
* Use +/- in upper-left to zoom.
* Use object in upper-right to change base map type.
* Use object in lower-left to make measurements on map.

