---
title: "Enger Park Tower & Observation Hill"
subtitle: "Duluth, MN"
---

Kim, [Cash](../shelties.html#cash) and I hiked from the [Enger Park](https://duluthmn.gov/parks/parks-listing/enger-park/) entrance, past the [Enger Park Tower](https://www.cbsnews.com/minnesota/news/enger-park-duluth-history/) and [Japanese Peace Bell](https://www.japanese-city.com/calendar/events/index.php?com=location&lID=2408) and [Garden](https://explorationvacation.net/enger-park-gardens-duluth-minnesota/) out to [Observation Hill](https://www.hikingproject.com/trail/7040160/observation-hill-duluth-traverse) on January 28, 2025. The trail was either part of the [Superior Hiking Trail](https://superiorhiking.org/) or the [Duluth Traverse Trail](https://duluthmn.gov/parks/parks-planning/progress-in-the-parks/duluth-traverse/) and offered some beautiful views of Lake Superior, the aerial lift bridge, and areas inland. The tower and Japanese Peace Bell and garden were also interesting. We will come ack in the summer so that we can climb the tower.

```{r setup, include=FALSE}
#| label: setup
#| include: false

# Make vector of colors for Iron River Area
clrs <- c("Highway"="#CC0000","Paved"="#336666",
          "Gravel"="#CC6600","Offroad"="#CC9900",
          "Trail"="#999933", "ATV"="#663300")

# Read in CSV file will all track info needed for the map
project <- "Minnesota"
walkID <- "MN_ENGER_OBS"
trkdat <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkdat.csv"))
trkinfo <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkinfo.csv"))

# Make the walk
walkIDs <- c("MNENGR11","MNENGR12","MNENGR13","MNENGR14","MNENGR15","MNENGR16",
             "MNENGR17","MNENGR17","MNENGR16","MNENGR15","MNENGR14","MNENGR13","MNENGR11")
awalk <- gpxhelpers::walkMaker(trkdat,trkinfo,walkIDs,findOrder=FALSE)

# Get photos
pix <- readxl::read_excel("c:/aaaPersonal/MAPPING/Data/Trail Mapping Info.xlsx",sheet="Photos")
walkPix <- gpxhelpers::walkGetPhotos(pix,walkIDs,"https://github.com/droglenc/MAPPING/raw/main/Images")
npix <- nrow(walkPix)
```

## Walk-Specific Map
```{r}
#| label: walkMap
#| echo: false
gpxhelpers::walkMap(awalk,clrs,verbose=FALSE)
```

:::{.callout-note appearance="simple"}
## Take Note
- Click on a segment to get specific information.
- Numeric labels correspond to the same labels in the elevation profile and summary information below.
:::

## Elevation Profile
```{r}
#| label: walkElevationConstruct
#| echo: false
#| results: hide
fnm <- paste0("c:/aaaWork/Web/droglenc.github.io/personal/Hiking/elevs/",walkID,".png") 
png(fnm,width=7,height=5,units="in",res=216)
gpxhelpers::walkElevation(awalk)
dev.off()
```
```{r}
#| label: walkElevation
#| echo: false
knitr::include_graphics(fnm)
```

## Images
```{r}
#| echo: false
#| results: asis
gpxhelpers::makeCarousel(id="Walk",path="",
                         imgs=walkPix$Photo,caps=walkPix$Caption,
                         width=75,captions=TRUE,controls=TRUE,indicators=FALSE)
```

## GPX Download
```{r}
#| label: gpxdownload
#| echo: false
#| message: false
#| results: asis
fnm <- paste0(walkID,".gpx")
gpxhelpers::makeWalkGPX(pin=paste0("c:/aaaPersonal/MAPPING/Tracks/",project),
                        pout="c:/aaaWork/Web/droglenc.github.io/personal/Hiking/gpx",
                        fnm=fnm,
                        IDs2Add=unique(walkIDs))
cat("A sanitized GPX file of our hike [is here](gpx/",fnm,").",sep="")
```

## Summary Information
```{r}
#| label: walkSummary
#| echo: false
gpxhelpers::walkSummary(awalk,dropOwner=TRUE)
```
