---
title: "Lookout Mountain Overlook"
subtitle: "Cascade River SP"
---

On January 3, 2026, Kim, [Cash](../shelties.html#cash), and I hiked the portion of the [Superior Hiking Trail](https://superiorhiking.org/trail-section/grand-marais-to-otter-lake-road/) in [Cascade River State Park](https://www.dnr.state.mn.us/state_parks/park.html?id=spk00133#homepage) from the parking area on Highway 61 out to Lookout Mountain. The trail is along the Cascade River gorge at first, with many beautiful waterfalls and plunge pools. It then turns away from the river and meanders through the woods until climbing to Lookout Mountain. A nice hike!

```{r}
#| label: setup
#| include: false

# Make vector of colors for Iron River Area
clrs <- c("Highway"="#CC0000","Paved"="#336666",
          "Gravel"="#CC6600","Offroad"="#CC9900",
          "Trail"="#999933", "ATV"="#663300")

# Read in CSV file will all track info needed for the map
project <- "Minnesota"
walkID <- "MN_CASCLOMTN"
trkdat <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkdat.csv"))
trkinfo <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkinfo.csv"))

# Make the walk
walkIDs <- c("MNCASCLO01","MNCASCLO02","MNCASCLO03","MNCASCLO04",
             "MNCASCLO04","MNCASCLO03","MNCASCLO02","MNCASCLO01")
awalk <- gpxhelpers::walkMaker(trkdat,trkinfo,walkIDs,findOrder=FALSE)

# Get photos
pix <- readxl::read_excel("c:/aaaPersonal/MAPPING/Data/Trail Mapping Info.xlsx",sheet="Photos")
walkPix <- gpxhelpers::walkGetPhotos(pix,walkIDs,"https://github.com/droglenc/MAPPING/raw/main/Images")
npix <- nrow(walkPix)
```

## Walk-Specific Map
```{r}
#| label: walkMap
#| echo: false
gpxhelpers::walkMap(awalk,clrs,verbose=FALSE)
```

:::{.callout-note appearance="simple"}
## Take Note
- Click on a segment to get specific information.
- Numeric labels correspond to the same labels in the elevation profile and summary information below.
:::

## Elevation Profile
```{r}
#| label: walkElevationConstruct
#| echo: false
#| results: hide
fnm <- paste0("c:/aaaWork/Web/droglenc.github.io/personal/Hiking/elevs/",walkID,".png") 
png(fnm,width=7,height=5,units="in",res=216)
gpxhelpers::walkElevation(awalk)
dev.off()
```
```{r}
#| label: walkElevation
#| echo: false
knitr::include_graphics(fnm)
```

## Images
```{r}
#| echo: false
#| results: asis
gpxhelpers::makeCarousel(id="Walk",path="",
                         imgs=walkPix$Photo,caps=walkPix$Caption,
                         width=75,captions=TRUE,controls=TRUE,indicators=FALSE)
```

## GPX Download
```{r}
#| label: gpxdownload
#| echo: false
#| message: false
#| results: asis
fnm <- paste0(walkID,".gpx")
gpxhelpers::makeWalkGPX(pin=paste0("c:/aaaPersonal/MAPPING/Tracks/",project),
                        pout="c:/aaaWork/Web/droglenc.github.io/personal/Hiking/gpx",
                        fnm=fnm,
                        IDs2Add=unique(walkIDs))
cat("A sanitized GPX file of our hike [is here](gpx/",fnm,").",sep="")
```

## Summary Information
```{r}
#| label: walkSummary
#| echo: false
gpxhelpers::walkSummary(awalk,dropOwner=TRUE)
```
