---
title: "Banyan Tree Loop"
subtitle: "Turtle Bay, Oahu, HI"
---

On April 9, 2026 Kim and I stopped at [Turtle Bay Resort](http://www.turtlebayresort.com/) on the North Shore of Oahu (near Kahuku) to get in a quick hike. We chose the [Banyan Tree Loop](https://www.alltrails.com/trail/hawaii/oahu/banyan-tree-route) which traversed through some of the resort area to a pillbox, then to [the famous Banyan Tree](https://petergreenberg.com/2014/07/26/movies-tv-shows-filmed-turtle-bay/), before looping back to the resort. It was an easy flat hike in the rain, but fun nevertheless.

```{r}
#| label: setup
#| include: false

project <- "Other"

## Run following two lines if new tracks have been added since last update
#source("c:/aaaPersonal/MAPPING/Scripts/dataPrepHelper.R")
#dat <- dataPrepHelper(project=project,basedir="c:/aaaPersonal/MAPPING/")

# Make vector of colors
clrs <- c("Highway"="#CC0000","Paved"="#336666",
          "Gravel"="#CC6600","Offroad"="#CC9900",
          "Trail"="#999933", "ATV"="#663300")

# Read in CSV file will all track info needed for the map
walkID <- "ON_BanyanTree"
trkdat <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkdat.csv"))
trkinfo <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkinfo.csv"))

# Make the walk
walkIDs <- c("BNTNTR01","BNTNTR02","BNTNTR04","BNTNTR05","BNTNTR07",
             "BNTNTR09","BNTNTR10","BNTNTR11","BNTNTR14","BNTNTR13",
             "BNTNTR12","BNTNTR09","BNTNTR08","BNTNTR06","BNTNTR03",
             "BNTNTR01")
awalk <- gpxhelpers::walkMaker(trkdat,trkinfo,walkIDs,findOrder=FALSE)

# Get photos
pix <- readxl::read_excel("c:/aaaPersonal/MAPPING/Data/Trail Mapping Info.xlsx",sheet="Photos")
walkPix <- gpxhelpers::walkGetPhotos(pix,walkIDs,"https://github.com/droglenc/MAPPING/raw/main/Images")
npix <- nrow(walkPix)
```

## Walk-Specific Map

```{r}
#| label: walkMap
#| echo: false
gpxhelpers::walkMap(awalk,clrs,verbose=FALSE)
```

## Elevation Profile
```{r}
#| label: walkElevationConstruct
#| echo: false
#| results: hide
fnm <- paste0("c:/aaaWork/Web/droglenc.github.io/personal/Hiking/elevs/",walkID,".png") 
png(fnm,width=7,height=5,units="in",res=216)
gpxhelpers::walkElevation(awalk,elev_bufr=0.1)
dev.off()
```
```{r}
#| label: walkElevation
#| echo: false
knitr::include_graphics(fnm)
```

## Images
```{r}
#| echo: false
#| results: asis
gpxhelpers::makeCarousel(id="Walk",path="",
                         imgs=walkPix$Photo,caps=walkPix$Caption,
                         width=75,captions=TRUE,controls=TRUE,indicators=FALSE)
```

## GPX Download
```{r}
#| label: gpxdownload
#| echo: false
#| message: false
#| results: asis
fnm <- paste0(walkID,".gpx")
gpxhelpers::makeWalkGPX(pin=paste0("c:/aaaPersonal/MAPPING/Tracks/",project),
                              pout="c:/aaaWork/Web/droglenc.github.io/personal/Hiking/gpx",
                              fnm=fnm,
                              IDs=unique(walkIDs))
cat("A sanitized GPX file of our hike [is here](gpx/",fnm,").",sep="")
```

## Summary Information
```{r}
#| label: walkSummary
#| echo: false
gpxhelpers::walkSummary(awalk,dropType=TRUE,dropOwner=TRUE)
```
