---
title: "City and Lake Walk"
subtitle: "Lucerne, Switzerland"
---

Our last few days in Switzerland were in Lucerne. We had a great hotel right on the river and spent the two days exploring the city and lake shore. On October 12, wfter a short walk through the city to get breakfast, we did a "city walk" that led to the ["Lion of Lucerne"](https://www.luzern.com/en/the-city/sights/top-sights/lion-monument), the [Church of St. Leodegar](https://www.luzern.com/en/the-city/sights/top-sights/church-of-st-leodegar), down to the lake to go past [Lido Lucerne](https://www.luzern.com/en/poi/lido-lucerne) before turning to walk along the lake back to our hotel. This was a fun and leisurely hike.

```{r}
#| label: setup
#| include: false

project <- "Other"

## Run following two lines if new tracks have been added since last update
#source("c:/aaaPersonal/MAPPING/Scripts/dataPrepHelper.R")
#dat <- dataPrepHelper(project=project,basedir="c:/aaaPersonal/MAPPING/")

# Make vector of colors for Iron River Area
clrs <- c("2022"="#CC0000","2023"="#CC6600","2024"="#CC9900")

# Read in CSV file will all track info needed for the map
walkID <- "ON_LCLW"
trkdat <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkdat.csv"))
trkinfo <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkinfo.csv"))

# Make the walk
walkIDs <- c("LCLW01","LCLW03","LCLW04","LCLW05","LCLW06",
             "LCLW07","LCLW08","LCLW10","LCLW10","LCLW09",
             "LCLW09","LCLW08","LCLW02","LCLW01")
awalk <- gpxhelpers::walkMaker(trkdat,trkinfo,walkIDs,findOrder=FALSE)

# Get photos
pix <- readxl::read_excel("c:/aaaPersonal/MAPPING/Data/Trail Mapping Info.xlsx",sheet="Photos")
walkPix <- gpxhelpers::walkGetPhotos(pix,walkIDs,"https://github.com/droglenc/MAPPING/raw/main/Images")
npix <- nrow(walkPix)
```

## Walk-Specific Map

```{r}
#| label: walkMap
#| echo: false
gpxhelpers::walkMap(awalk,clrs,verbose=FALSE)
```

## Elevation Profile
```{r}
#| label: walkElevationConstruct
#| echo: false
#| results: hide
fnm <- paste0("c:/aaaWork/Web/droglenc.github.io/personal/Hiking/elevs/",walkID,".png") 
png(fnm,width=7,height=5,units="in",res=216)
gpxhelpers::walkElevation(awalk)
dev.off()
```
```{r}
#| label: walkElevation
#| echo: false
knitr::include_graphics(fnm)
```

## Images
```{r}
#| echo: false
#| results: asis
gpxhelpers::makeCarousel(id="Walk",path="",
                         imgs=walkPix$Photo,caps=walkPix$Caption,
                         width=75,captions=TRUE,controls=TRUE,indicators=FALSE)
```

## GPX Download
```{r}
#| label: gpxdownload
#| echo: false
#| message: false
#| results: asis
fnm <- paste0(walkID,".gpx")
gpxhelpers::makeWalkGPX(pin=paste0("c:/aaaPersonal/MAPPING/Tracks/",project),
                        pout="c:/aaaWork/Web/droglenc.github.io/personal/Hiking/gpx",
                        fnm=fnm,
                        IDs=unique(walkIDs))
cat("A sanitized GPX file of our hike [is here](gpx/",fnm,").",sep="")
```

## Summary Information
```{r}
#| label: walkSummary
#| echo: false
gpxhelpers::walkSummary(awalk,dropType=TRUE,dropOwner=TRUE)
```
