---
title: "St. Luzikapelle and Mittenberg Loop"
subtitle: "Chur, Switzerland"
---

On our second full day in Switzerland (October 6, 2024) we had made our way to the historic city of [Chur](https://www.chur.graubuenden.ch/en), the oldest city in Switzerland. While we did make a [city walk](ON_CHURCW.html) the next day, we were itching to get into the countryside. The trail we decided on started on the edge of town fairly near our hotel and quick climbed via several switchbacks through beautiful woods to [St. Luzikapelle](https://www.chur.graubuenden.ch/en/attractions/st-luzi-chapel-0), a beautiful little chapel in a rock grotto. From there we continued to climb until we reached an alpine meadow near Mittenberg. This area screamed "Sound of Music", and the overlook to the north and west was stunning. From there was a nice descent (with lots of switchbacks) back to Chur. This hike was a great introduction to the Swiss landscape, we are glad we did it.

```{r}
#| label: setup
#| include: false

project <- "Switzerland"

## Run following two lines if new tracks have been added since last update
#source("c:/aaaPersonal/MAPPING/Scripts/dataPrepHelper.R")
#dat <- dataPrepHelper(project=project,basedir="c:/aaaPersonal/MAPPING/")

# Make vector of colors for Iron River Area
clrs <- c("2022"="#CC0000","2023"="#CC6600","2024"="#CC9900")

# Read in CSV file will all track info needed for the map
walkID <- "ON_STLUZI"
trkdat <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkdat.csv"))
trkinfo <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkinfo.csv"))

# Make the walk
walkIDs <- c("STLU01","STLU02","STLU03","STLU04","STLU05",
             "STLUA","STLUA","STLU06","STLU07","STLU08",
             "STLU09","STLU10","STLU11","STLU12","STLU13",
             "STLU14","STLU15","STLU01")
awalk <- gpxhelpers::walkMaker(trkdat,trkinfo,walkIDs,findOrder=FALSE)

# Get photos
pix <- readxl::read_excel("c:/aaaPersonal/MAPPING/Data/Trail Mapping Info.xlsx",sheet="Photos")
walkPix <- gpxhelpers::walkGetPhotos(pix,walkIDs,"https://github.com/droglenc/MAPPING/raw/main/Images")
npix <- nrow(walkPix)
```

## Walk-Specific Map

```{r}
#| label: walkMap
#| echo: false
gpxhelpers::walkMap(awalk,clrs,verbose=FALSE)
```

## Elevation Profile
```{r}
#| label: walkElevationConstruct
#| echo: false
#| results: hide
fnm <- paste0("c:/aaaWork/Web/droglenc.github.io/personal/Hiking/elevs/",walkID,".png") 
png(fnm,width=7,height=5,units="in",res=216)
gpxhelpers::walkElevation(awalk)
dev.off()
```
```{r}
#| label: walkElevation
#| echo: false
knitr::include_graphics(fnm)
```

## Images
```{r}
#| echo: false
#| results: asis
gpxhelpers::makeCarousel(id="Walk",path="",
                         imgs=walkPix$Photo,caps=walkPix$Caption,
                         width=75,captions=TRUE,controls=TRUE,indicators=FALSE)
```

## GPX Download
```{r}
#| label: gpxdownload
#| echo: false
#| message: false
#| results: asis
fnm <- paste0(walkID,".gpx")
gpxhelpers::makeWalkGPX(pin=paste0("c:/aaaPersonal/MAPPING/Tracks/",project),
                        pout="c:/aaaWork/Web/droglenc.github.io/personal/Hiking/gpx",
                        fnm=fnm,
                        IDs=unique(walkIDs))
cat("A sanitized GPX file of our hike [is here](gpx/",fnm,").",sep="")
```

## Summary Information
```{r}
#| label: walkSummary
#| echo: false
gpxhelpers::walkSummary(awalk,dropType=TRUE,dropOwner=TRUE)
```
