---
title: "Trummelbach Falls Loop"
subtitle: "Lauterbrunnen, Switzerland"
---

On our First day in [Lauterbrunnen](https://www.myswitzerland.com/en-us/destinations/lauterbrunnen/) (October 10, 2024) we left our [hotel](https://www.silberhorn.com/en/) to walk through the city and countryside to the [Trummelbach waterfalls](https://fullsuitcase.com/trummelbach-falls/). Lauterbrunnen is stunningly beautiful sitting in deep valley with steep walls. Thus, the hike to Trummelback was jaw-dropping gorgeous in every direction. We stopped along the way to view [Staubbach Falls](https://www.myswitzerland.com/en-us/experiences/staubbach-falls-free-falling-waters-with-a-mist-of-spray/) up close, as there is a side trail passing through a tunnel that gets you in the spray of this highest (297 m) free-falling waterfall in Switzerland! From there it is a leisurely walk on roads (not busy) or trails to the entrance to Trummelbach Falls. The Trummelbach waterfalls are Europe's largest subterranean water falls. The falls can be viewed from a number of different vantage points that are connected with underground paths, platforms, and a lift. Access to the falls was well worth the $15CHF entry fee. Following the falls we returned to the main town and our hotel using a slight different route that was less busy and mostly followed the river. This was a great hike and experience!!

```{r}
#| label: setup
#| include: false

project <- "Other"

## Run following two lines if new tracks have been added since last update
#source("c:/aaaPersonal/MAPPING/Scripts/dataPrepHelper.R")
#dat <- dataPrepHelper(project=project,basedir="c:/aaaPersonal/MAPPING/")

# Make vector of colors for Iron River Area
clrs <- c("2022"="#CC0000","2023"="#CC6600","2024"="#CC9900")

# Read in CSV file will all track info needed for the map
walkID <- "ON_TRUMMELBACH"
trkdat <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkdat.csv"))
trkinfo <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkinfo.csv"))

# Make the walk
walkIDs <- c("TRMBF01","TRMBF02","TRMBF03","TRMBF03","TRMBF04",
             "TRMBF05","TRMBF06","TRMBF06","TRMBF05","TRMBF07",
             "TRMBF01")
awalk <- gpxhelpers::walkMaker(trkdat,trkinfo,walkIDs,findOrder=FALSE)

# Get photos
pix <- readxl::read_excel("c:/aaaPersonal/MAPPING/Data/Trail Mapping Info.xlsx",sheet="Photos")
walkPix <- gpxhelpers::walkGetPhotos(pix,walkIDs,"https://github.com/droglenc/MAPPING/raw/main/Images")
npix <- nrow(walkPix)
```

## Walk-Specific Map

```{r}
#| label: walkMap
#| echo: false
gpxhelpers::walkMap(awalk,clrs,verbose=FALSE)
```

## Elevation Profile
```{r}
#| label: walkElevationConstruct
#| echo: false
#| results: hide
fnm <- paste0("c:/aaaWork/Web/droglenc.github.io/personal/Hiking/elevs/",walkID,".png") 
png(fnm,width=7,height=5,units="in",res=216)
gpxhelpers::walkElevation(awalk)
dev.off()
```
```{r}
#| label: walkElevation
#| echo: false
knitr::include_graphics(fnm)
```

## Images
```{r}
#| echo: false
#| results: asis
gpxhelpers::makeCarousel(id="Walk",path="",
                         imgs=walkPix$Photo,caps=walkPix$Caption,
                         width=75,captions=TRUE,controls=TRUE,indicators=FALSE)
```

## GPX Download
```{r}
#| label: gpxdownload
#| echo: false
#| message: false
#| results: asis
fnm <- paste0(walkID,".gpx")
gpxhelpers::makeWalkGPX(pin=paste0("c:/aaaPersonal/MAPPING/Tracks/",project),
                        pout="c:/aaaWork/Web/droglenc.github.io/personal/Hiking/gpx",
                        fnm=fnm,
                        IDs=unique(walkIDs))
cat("A sanitized GPX file of our hike [is here](gpx/",fnm,").",sep="")
```

## Summary Information
```{r}
#| label: walkSummary
#| echo: false
gpxhelpers::walkSummary(awalk,dropType=TRUE,dropOwner=TRUE)
```
