---
title: "Zmutt Loop"
subtitle: "Zermatt, Switzerland"
---

Out first full day in Zermatt (October 8, 2024) was mostly cloudy and rainy. As such we decided to save the [Gornergrat hike](ON GORNERGRAT.html) for the next day in hopes that the clouds would clear and we could see the Matterhorn. On this day then we began a hike in Zermatt that passed through Zmutt, Zmutt See, and Blatten before looping back to Zermatt. The hike up to Zmutt was classic Switzerland through woods, alpine meadows, and rustic areas with local's cabins, while all the while hearing the dinging of livestock bells and the murmur of distant waterfalls. The trail back after crossing the Zmuttback was initially less interesting as we were on a downhill ski run. Eventually we left that and returned to a more woodsy and pastoral trail leading to the neat little towns of Zum See (we wished the restaurant would have been open, but we were off season) and Blatten. The trail after Blatten curled through some woods before crossing the river to return to Zermatt. This was a great trail to see the Swiss landscape on a rainy day. Unfortunately, we did not take a lot of pictures because of the rain.

```{r}
#| label: setup
#| include: false

project <- "Other"

## Run following two lines if new tracks have been added since last update
#source("c:/aaaPersonal/MAPPING/Scripts/dataPrepHelper.R")
#dat <- dataPrepHelper(project=project,basedir="c:/aaaPersonal/MAPPING/")

# Make vector of colors for Iron River Area
clrs <- c("2022"="#CC0000","2023"="#CC6600","2024"="#CC9900")

# Read in CSV file will all track info needed for the map
walkID <- "ON_ZMUTT"
trkdat <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkdat.csv"))
trkinfo <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkinfo.csv"))

# Make the walk
walkIDs <- c("ZMUTT1","ZMUTT2","ZMUTT3","ZMUTTA","ZMUTTA",
             "ZMUTT4","ZMUTT5","ZMUTT6","ZMUTTB","ZMUTTB",
             "ZMUTT7","ZMUTT8","ZMUTT9","ZMUTT1")
awalk <- gpxhelpers::walkMaker(trkdat,trkinfo,walkIDs,findOrder=FALSE)

# Get photos
pix <- readxl::read_excel("c:/aaaPersonal/MAPPING/Data/Trail Mapping Info.xlsx",sheet="Photos")
walkPix <- gpxhelpers::walkGetPhotos(pix,walkIDs,"https://github.com/droglenc/MAPPING/raw/main/Images")
npix <- nrow(walkPix)
```

## Walk-Specific Map

*Hint: Change map layer to "Imagery" using the object in the upper-right corner of the map below.*

```{r}
#| label: walkMap
#| echo: false
gpxhelpers::walkMap(awalk,clrs,verbose=FALSE)
```

## Elevation Profile
```{r}
#| label: walkElevationConstruct
#| echo: false
#| results: hide
fnm <- paste0("c:/aaaWork/Web/droglenc.github.io/personal/Hiking/elevs/",walkID,".png") 
png(fnm,width=7,height=5,units="in",res=216)
gpxhelpers::walkElevation(awalk)
dev.off()
```
```{r}
#| label: walkElevation
#| echo: false
knitr::include_graphics(fnm)
```

## Images
```{r}
#| echo: false
#| results: asis
gpxhelpers::makeCarousel(id="Walk",path="",
                         imgs=walkPix$Photo,caps=walkPix$Caption,
                         width=75,captions=TRUE,controls=TRUE,indicators=FALSE)
```

## GPX Download
```{r}
#| label: gpxdownload
#| echo: false
#| message: false
#| results: asis
fnm <- paste0(walkID,".gpx")
gpxhelpers::makeWalkGPX(pin=paste0("c:/aaaPersonal/MAPPING/Tracks/",project),
                        pout="c:/aaaWork/Web/droglenc.github.io/personal/Hiking/gpx",
                        fnm=fnm,
                        IDs=unique(walkIDs))
cat("A sanitized GPX file of our hike [is here](gpx/",fnm,").",sep="")
```

## Summary Information
```{r}
#| label: walkSummary
#| echo: false
gpxhelpers::walkSummary(awalk,dropType=TRUE,dropOwner=TRUE)
```
