---
title: "Black Top Mesa from First Water TH"
subtitle: "Dutchman's & Second Water Trail Loop"
---

On March 9, 2022 Kim and I hiked to Black Top Mesa from the First Water trailhead via Dutchman's and Bull Pass trails. This was a long walk for us (~12.5 mi) but offered stunning views of Weaver's Needle from the north, which we had not seen before. The climb up to the top was steep but the trail was fairly easy to navigate. We returned to the trailhead via the Black Mesa and Second Water trails. There were many more cacti no the trail back. Fun hike. Details are below.

```{r}
#| label: setup
#| include: false

# Make vector of colors for Iron River Area
clrs <- c("2022"="#CC0000","2023"="#CC6600")

# Read in CSV file will all track info needed for the map
project <- "Superstition Wilderness"
trkdat <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkdat.csv"))
trkinfo <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkinfo.csv"))

# Make the walk
walkIDs <- c("BMSA01","BMSA02","BMSA03","BMSA04","BMSA05","BMSA06","BMSA07","BMSA08",
             "BMSA08","BMSA07","BMSA06","BMSA05","BMSA10","BMSA11","BMSA12","BMSA13",
             "BMSA01")
awalk <- gpxhelpers::walkMaker(trkdat,trkinfo,walkIDs,findOrder=FALSE)

# Write the walk out to a gpx file for downloading
gpxhelpers::combineTracks2GPX(pin="c:/aaaPersonal/MAPPING/Tracks/Superstition Wilderness",
                              pout="c:/aaaWork/Web/droglenc.github.io/personal/Hiking/gpx",
                              fnm="SW_BlackTopMesa_2022.gpx",
                              IDs=unique(walkIDs))

# Get photos
pix <- readxl::read_excel("c:/aaaPersonal/MAPPING/Data/Trail Mapping Info.xlsx",sheet="Photos")
walkPix <- gpxhelpers::walkGetPhotos(pix,walkIDs,"https://github.com/droglenc/MAPPING/raw/main/Images")
npix <- nrow(walkPix)
```

## Overview Map
The extent of this walk is highlighted by the blue box in this map.

```{r}
#| label: overviewMap
#| echo: false
gpxhelpers::allTracksMap(trkdat,clrs,walk=awalk,verbose=FALSE,map_bufr=0.0008)
```

:::{.callout-info appearance="simple"}
## Map Key
See [Superstition Wilderness Overview page](gpx/Superstition Wilderness.html) for segment color coding key and description for use of controls.
:::

## Walk-Specific Map
```{r}
#| label: walkMap
#| echo: false
gpxhelpers::walkMap(awalk,clrs,verbose=FALSE)
```

:::{.callout-note appearance="simple"}
## Take Note
- Click on a segment to get specific information.
- Numeric labels correspond to the same labels in the elevation profile and summary information below.
:::

## Elevation Profile
```{r}
#| label: walkElevation
#| echo: false
gpxhelpers::walkElevation(awalk)
```

## Summary Information
```{r}
#| label: walkSummary
#| echo: false
gpxhelpers::walkSummary(awalk)
```

## Images
```{r}
#| echo: false
#| results: asis
gpxhelpers::makeCarousel(id="Walk",path="",
                         imgs=walkPix$Photo,caps=walkPix$Caption,
                         width=75,captions=TRUE,controls=TRUE,indicators=FALSE)
```

## GPX Download
A sanitized GPX file of our hike [is here](gpx/SW_BlackTopMesa_2022.gpx).
