---
title: "Superstition Ridgeline West"
subtitle: "Hieroglyphics TH to Siphon Draw"
---

On February 10, 2025 Kim and I hiked the western portion of the Superstition Ridgeline. We climbed to the Ridgeline trail via Hieroglyphics Trail and then turned west to Siphon Draw which we descended. We had a little trouble finding the trail at first (in retrospect, not sure how we missed it) and a few other places we had to search a little, but otherwise it was pretty easy to follow. The views were simply amazing, in all directions!! The only downside is that Siphon Draw is a tough descent when your legs are tired. This was a half of a bucket-list hike; we hope to do the East end (and visit Superstition Peak) next year.

```{r}
#| label: setup
#| include: false

# Make vector of colors
clrs <- c("Road"="#CC0000","Numbered"="#CC6600","Named"="#CC9900","Unnamed"="#663300")

# Read in CSV file will all track info needed for the map
project <- "Superstition Wilderness"
## Run following two lines if new tracks have been added since last update
#source("c:/aaaPersonal/MAPPING/Scripts/dataPrepHelper.R")
#dat <- dataPrepHelper(project=project,basedir="c:/aaaPersonal/MAPPING/")

walkID <- "SW_Ridgeline H2SD"
trkdat <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkdat.csv"))
trkinfo <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkinfo.csv"))

# Make the walk
walkIDs <- c("HRGPH01","HRGPH02","HRGPH03","RDGLIN21","RDGLIN22",
             "SPHNDR10","JCBCUT12","CNJCUT10")
awalk <- gpxhelpers::walkMaker(trkdat,trkinfo,walkIDs,findOrder=FALSE)

# Get photos
pix <- readxl::read_excel("c:/aaaPersonal/MAPPING/Data/Trail Mapping Info.xlsx",sheet="Photos")
walkPix <- gpxhelpers::walkGetPhotos(pix,walkIDs,"https://github.com/droglenc/MAPPING/raw/main/Images")
npix <- nrow(walkPix)
```

## Walk-Specific Map
See [Superstition Wilderness Overview page](Superstition Wilderness.html) for an overview map of all hikes.

```{r}
#| label: walkMap
#| echo: false
gpxhelpers::walkMap(awalk,clrs,verbose=FALSE)
```

:::{.callout-note appearance="simple"}
## Take Note
- Click on a segment to get specific information.
- Numeric labels correspond to the same labels in the elevation profile and summary information below.
- See [Superstition Wilderness Overview page](Superstition Wilderness.html) for description of use of controls.
:::

## Elevation Profile
```{r}
#| label: walkElevationConstruct
#| echo: false
#| results: hide
fnm <- paste0("c:/aaaWork/Web/droglenc.github.io/personal/Hiking/elevs/",walkID,".png") 
png(fnm,width=7,height=5,units="in",res=216)
gpxhelpers::walkElevation(awalk)
dev.off()
```
```{r}
#| label: walkElevation
#| echo: false
knitr::include_graphics(fnm)
```

## Images
```{r}
#| echo: false
#| results: asis
gpxhelpers::makeCarousel(id="Walk",path="",
                         imgs=walkPix$Photo,caps=walkPix$Caption,
                         width=75,captions=TRUE,controls=TRUE,indicators=FALSE)
```

## GPX Download
```{r}
#| label: gpxdownload
#| echo: false
#| message: false
#| results: asis
fnm <- paste0(walkID,".gpx")
gpxhelpers::makeWalkGPX(pin=paste0("c:/aaaPersonal/MAPPING/Tracks/",project),
                              pout="c:/aaaWork/Web/droglenc.github.io/personal/Hiking/gpx",
                              fnm=fnm,
                              IDs=unique(walkIDs))
cat("A sanitized GPX file of our hike [is here](gpx/",fnm,").",sep="")
```

## Summary Information
```{r}
#| label: walkSummary
#| echo: false
gpxhelpers::walkSummary(awalk,dropType=TRUE,dropOwner=TRUE)
```
