---
title: "Wave Cave"
subtitle: "Lost Goldmine & Carney Springs Trails"
---

On March 6, 2022 Kim and I hiked from the first Peralta Trailhead parking area to the "Wave Cave" via the Lost Goldmine, Carney Springs, and Wave Cave trails. The trail was fairly flat until the Wave Cave trail portion, which ascended quickly. The actual cave was larger than I expected and offered up some great photos. There were a decent number of people on the trail on this beautiful day. Details are below.

```{r}
#| label: setup
#| include: false

# Make vector of colors for Iron River Area
clrs <- c("2022"="#CC0000","2023"="#CC6600")

# Read in CSV file will all track info needed for the map
project <- "Superstition Wilderness"
trkdat <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkdat.csv"))
trkinfo <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkinfo.csv"))

# Make the walk
walkIDs <- c("WVCV01","WVCV02","WVCV03","WVCV04","WVCV04","WVCV03","WVCV02","WVCV01")
awalk <- gpxhelpers::walkMaker(trkdat,trkinfo,walkIDs,findOrder=FALSE)

# Write the walk out to a gpx file for downloading
gpxhelpers::combineTracks2GPX(pin="c:/aaaPersonal/MAPPING/Tracks/Superstition Wilderness",
                              pout="c:/aaaWork/Web/droglenc.github.io/personal/Hiking/gpx",
                              fnm="SW_WaveCave_2022.gpx",
                              IDs=unique(walkIDs))

# Get photos
pix <- readxl::read_excel("c:/aaaPersonal/MAPPING/Data/Trail Mapping Info.xlsx",sheet="Photos")
walkPix <- gpxhelpers::walkGetPhotos(pix,walkIDs,"https://github.com/droglenc/MAPPING/raw/main/Images")
npix <- nrow(walkPix)
```

## Overview Map
The extent of this walk is highlighted by the blue box in this map.

```{r}
#| label: overviewMap
#| echo: false
gpxhelpers::allTracksMap(trkdat,clrs,walk=awalk,verbose=FALSE,map_bufr=0.0004)
```

:::{.callout-info appearance="simple"}
## Map Key
See [Superstition Wilderness Overview page](Superstition Wilderness.html) for segment color coding key and description for use of controls.
:::

## Walk-Specific Map
```{r}
#| label: walkMap
#| echo: false
gpxhelpers::walkMap(awalk,clrs,verbose=FALSE)
```

:::{.callout-note appearance="simple"}
## Take Note
- Click on a segment to get specific information.
- Numeric labels correspond to the same labels in the elevation profile and summary information below.
:::

## Elevation Profile
```{r}
#| label: walkElevation
#| echo: false
gpxhelpers::walkElevation(awalk)
```

## Summary Information
```{r}
#| label: walkSummary
#| echo: false
gpxhelpers::walkSummary(awalk)
```

## Images
```{r}
#| label: walkPix
#| echo: false
#| results: asis
gpxhelpers::makeCarousel(id="Walk",path="",
                         imgs=walkPix$Photo,caps=walkPix$Caption,
                         width=75,captions=TRUE,controls=TRUE,indicators=FALSE)
```

## GPX Download
A sanitized GPX file of our hike [is here](gpx/SW_WaveCave_2022.gpx).
