---
title: "Little Manitou Falls via Beaver Trail"
subtitle: "Pattison State Park"
---

On May 1, 2023 Kim, [Cash](../shelties.html#cash) and I explored around [Pattison State Park](https://dnr.wisconsin.gov/topic/parks/pattison). We initially walked over to [Big Manitou Falls](https://en.wikipedia.org/wiki/Big_Manitou_Falls), but I did not map that part for some reason. We then followed the Beaver Trail on the west side of Interfalls Lake out to the Little Manitou Falls trail to Little Manitou Falls. We got some great pictures of Cash there before backtracking, crossing the CCC Bridge, and following the Beaver Trail on the east side of Interfalls Lake back to the parking area. All-in-all a fun day.

```{r}
#| label: setup
#| include: false
## Run code in "Wisconsin.qmd" if tracks have been updated
project <- "Wisconsin"

# Make vector of colors
clrs <- c("Highway"="#CC0000","Paved"="#336666","Gravel"="#CC6600",
          "Offroad"="#CC9900","Trail"="#999933", "ATV"="#663300")

# Read in CSV file will all track info needed for the map
walkID <- "WI_Little_Manitou"
trkdat <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkdat.csv"))
trkinfo <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkinfo.csv"))

# Make the walk
walkIDs <- c("PSPBVR02","PSPLMF01","PSPLMF01","PSPBVR05")
awalk <- gpxhelpers::walkMaker(trkdat,trkinfo,walkIDs,findOrder=FALSE)

# Get photos
pix <- readxl::read_excel("c:/aaaPersonal/MAPPING/Data/Trail Mapping Info.xlsx",sheet="Photos")
walkPix <- gpxhelpers::walkGetPhotos(pix,walkIDs,"https://github.com/droglenc/MAPPING/raw/main/Images")
npix <- nrow(walkPix)
```

## Walk-Specific Map

```{r}
#| label: walkMap
#| echo: false
gpxhelpers::walkMap(awalk,clrs,verbose=FALSE)
```

## Elevation Profile
```{r}
#| label: walkElevationConstruct
#| echo: false
#| results: hide
fnm <- paste0("c:/aaaWork/Web/droglenc.github.io/personal/Hiking/elevs/",walkID,".png") 
png(fnm,width=7,height=5,units="in",res=216)
gpxhelpers::walkElevation(awalk)
dev.off()
```
```{r}
#| label: walkElevation
#| echo: false
knitr::include_graphics(fnm)
```

## Images
```{r}
#| echo: false
#| results: asis
gpxhelpers::makeCarousel(id="Walk",path="",
                         imgs=walkPix$Photo,caps=walkPix$Caption,
                         width=75,captions=TRUE,controls=TRUE,indicators=FALSE)
```

## GPX Download
```{r}
#| label: gpxdownload
#| echo: false
#| message: false
#| results: asis
fnm <- paste0(walkID,".gpx")
gpxhelpers::makeWalkGPX(pin=paste0("c:/aaaPersonal/MAPPING/Tracks/",project),
                              pout="c:/aaaWork/Web/droglenc.github.io/personal/Hiking/gpx",
                              fnm=fnm,
                              IDs=unique(walkIDs))
cat("A sanitized GPX file of our hike [is here](gpx/",fnm,").",sep="")
```

## Summary Information
```{r}
#| label: walkSummary
#| echo: false
gpxhelpers::walkSummary(awalk,dropType=TRUE,dropOwner=TRUE)
```
