---
title: "Makwa Ziibiins Miikana Trail"
subtitle: "Superior, WI"
---

On April 26, 2022 [Cash](../shelties.html#cash) and I hiked the [Makwa Ziibiins Miikana Trail](https://wisconsinharbortowns.net/places/superior/makwa-ziibiins-miikana-bear-creek-trail/) in Superior, WI. This is a fun little trail from the edge of town out to wetlands on Allouez Bay. When we were there they were just starting to build a floating boardwalk through the wetlands to connect with Wisconsin Point. My understanding is that it is now complete. We will have to do this trail again.

```{r}
#| label: setup
#| include: false
## Run code in "Wisconsin.qmd" if tracks have been updated
project <- "Wisconsin"

# Make vector of colors
clrs <- c("Highway"="#CC0000","Paved"="#336666","Gravel"="#CC6600",
          "Offroad"="#CC9900","Trail"="#999933", "ATV"="#663300")

# Read in CSV file will all track info needed for the map
walkID <- "WI_Makwa_Ziibiins"
trkdat <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkdat.csv"))
trkinfo <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkinfo.csv"))

# Make the walk
walkIDs <- c("WIMZM01","WIMZM02","WIMZM03","WIMZM04","WIMZM04",
             "WIMZM05","WIMZM06","WIMZM06","WIMZM05","WIMZM03",
             "WIMZM02","WIMZM01")
awalk <- gpxhelpers::walkMaker(trkdat,trkinfo,walkIDs,findOrder=FALSE)

# Get photos
pix <- readxl::read_excel("c:/aaaPersonal/MAPPING/Data/Trail Mapping Info.xlsx",sheet="Photos")
walkPix <- gpxhelpers::walkGetPhotos(pix,walkIDs,"https://github.com/droglenc/MAPPING/raw/main/Images")
npix <- nrow(walkPix)
```

## Walk-Specific Map

```{r}
#| label: walkMap
#| echo: false
gpxhelpers::walkMap(awalk,clrs,verbose=FALSE)
```

## Elevation Profile
```{r}
#| label: walkElevationConstruct
#| echo: false
#| results: hide
fnm <- paste0("c:/aaaWork/Web/droglenc.github.io/personal/Hiking/elevs/",walkID,".png") 
png(fnm,width=7,height=5,units="in",res=216)
gpxhelpers::walkElevation(awalk)
dev.off()
```
```{r}
#| label: walkElevation
#| echo: false
knitr::include_graphics(fnm)
```

## Images
```{r}
#| echo: false
#| results: asis
gpxhelpers::makeCarousel(id="Walk",path="",
                         imgs=walkPix$Photo,caps=walkPix$Caption,
                         width=75,captions=TRUE,controls=TRUE,indicators=FALSE)
```

## GPX Download
```{r}
#| label: gpxdownload
#| echo: false
#| message: false
#| results: asis
fnm <- paste0(walkID,".gpx")
gpxhelpers::makeWalkGPX(pin=paste0("c:/aaaPersonal/MAPPING/Tracks/",project),
                              pout="c:/aaaWork/Web/droglenc.github.io/personal/Hiking/gpx",
                              fnm=fnm,
                              IDs=unique(walkIDs))
cat("A sanitized GPX file of our hike [is here](gpx/",fnm,").",sep="")
```

## Summary Information
```{r}
#| label: walkSummary
#| echo: false
gpxhelpers::walkSummary(awalk,dropType=TRUE,dropOwner=TRUE)
```
