---
title: "Newport State Park"
---

The "big" hike on our first full day in Door County was at [Newport State Park](https://dnr.wisconsin.gov/topic/parks/newport). We decided to hike out to [Europe Bay WOods State Natural Area](https://dnr.wisconsin.gov/topic/statenaturalareas/EuropeBayWoods) via the Europe Bay and Lynd Point trails. We returned on the Hotz and other portions (mostly) of the Europe Bay trail. We got some great scenery with Lake Michigan proper to our right for the first "half" of the hike and some inland wetlands for a portion of the second "half" of the hike. This was a fun hike.

```{r}
#| label: setup
#| include: false
## Run code in "Wisconsin.qmd" if tracks have been updated
project <- "Wisconsin"

# Make vector of colors
clrs <- c("Highway"="#CC0000","Paved"="#336666","Gravel"="#CC6600",
          "Offroad"="#CC9900","Trail"="#999933", "ATV"="#663300")

# Read in CSV file will all track info needed for the map
walkID <- "WI_Newport"
trkdat <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkdat.csv"))
trkinfo <- read.csv(paste0("c:/aaaPersonal/MAPPING/Data/",project,"_trkinfo.csv"))

# Make the walk
walkIDs <- c("DCNPEUBY01","DCNPLYPT01","DCNPLYPT02","DCNPLYPT02","DCNPLYPT03",
             "DCNPEUBY03","DCNPEUBY04","DCNPEUBY06","DCNPEUBY07","DCNPHOTZ01",
             "DCNPEUBY06","DCNPEUBY05","DCNPEUBY03","DCNPEUBY02","DCNPEUBY01")
awalk <- gpxhelpers::walkMaker(trkdat,trkinfo,walkIDs,findOrder=FALSE)

# Get photos
pix <- readxl::read_excel("c:/aaaPersonal/MAPPING/Data/Trail Mapping Info.xlsx",sheet="Photos")
walkPix <- gpxhelpers::walkGetPhotos(pix,walkIDs,"https://github.com/droglenc/MAPPING/raw/main/Images")
npix <- nrow(walkPix)
```

## Walk-Specific Map

```{r}
#| label: walkMap
#| echo: false
gpxhelpers::walkMap(awalk,clrs,verbose=FALSE)
```

## Elevation Profile
```{r}
#| label: walkElevationConstruct
#| echo: false
#| results: hide
fnm <- paste0("c:/aaaWork/Web/droglenc.github.io/personal/Hiking/elevs/",walkID,".png") 
png(fnm,width=7,height=5,units="in",res=216)
gpxhelpers::walkElevation(awalk)
dev.off()
```
```{r}
#| label: walkElevation
#| echo: false
knitr::include_graphics(fnm)
```

## Images
```{r}
#| echo: false
#| results: asis
gpxhelpers::makeCarousel(id="Walk",path="",
                         imgs=walkPix$Photo,caps=walkPix$Caption,
                         width=75,captions=TRUE,controls=TRUE,indicators=FALSE)
```

## GPX Download
```{r}
#| label: gpxdownload
#| echo: false
#| message: false
#| results: asis
fnm <- paste0(walkID,".gpx")
gpxhelpers::makeWalkGPX(pin=paste0("c:/aaaPersonal/MAPPING/Tracks/",project),
                              pout="c:/aaaWork/Web/droglenc.github.io/personal/Hiking/gpx",
                              fnm=fnm,
                              IDs=unique(walkIDs))
cat("A sanitized GPX file of our hike [is here](gpx/",fnm,").",sep="")
```

## Summary Information
```{r}
#| label: walkSummary
#| echo: false
gpxhelpers::walkSummary(awalk,dropType=TRUE,dropOwner=TRUE)
```
